Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
casi listo

\begin{figure*}
\begin{center}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

\caption{\textbf{Comparison between simulations and observations.}  
  \label{fig:muse}}
\end{figure}

@@

The Monte Carlo code we use (CLARA)  follows the propagation of
individual photons through a neutral Hydrogen medium characterized by
its temperature, velocity field and global optical depth.
The code assumes an homogeneous density throughout the simulated
volume.
In the current implementation we neglect the influence of dust.
Our basic model is an spherical distribution of neutral hydrogen,
an approximation commonly used in the literature, as it explains a
wide variety of observational features
\citep{Ahn03,Verhamme06,Dijkstra06}.

@@

\begin{equation}
	v_{x}=\frac{x}{R}V_{\rm out}-\frac{y}{R}V_{\rm rot} ,
	\label{eq:vx}
\end{equation}

\begin{equation}
	v_{y}=\frac{y}{R}V_{\rm out}+\frac{x}{R}V_{\rm rot} ,
	\label{eq:vy}
\end{equation}

\begin{equation}
	v_{z}=\frac{z}{R}V_{\rm out},
	\label{eq:vz}
\end{equation}
%
where $x$, $y$ and $z$ are the cartesian position coordinates with the
origin at the sphere's center, $R$ is the radius of the sphere and the
direction of the angular velocity vector corresponds to the $\hat{k}$
unit vector.

@@

\begin{equation}
x' = x + \frac{\vec{V}_{\rm rot}\cdot\hat{k}}{v_{\rm th}}
\label{eq:shift_x}
\end{equation}
%
where $x'$ is the photon's new frequency, $x$ is the photon's
frequency after being procesed by the outflow, $v_{\rm rot}$ is the 
rotational velocity at the point of escape of the photon, $\hat{k}$ is
the photon's direction of propagation and $v_{\rm th}$ is the thermal
velocity of the sphere.

@@

\subsection{Theoretical Insights}

A first approach to an analytical expression that returns the \lya spectrum
from a rotating galaxy is presented by \cite{Garavito14}.
This derivation is based on the assumption that the distribution of
photons' propagation directions at the edge of the galaxy is
anisotropic and depends of \tauh only. 
So this approximation becomes more accurate with higher optical depth
and it is also the reason why the Doppler Shift technique to induce
rotational effects to an outflow \lya spectrum works.

\subsection{Links to observations}

There are at least three inmmediate ways the work we have presented
here can be useful to observational efforts.

@@

To address the first questionswe posed in the introduction (What is then
the expected imprint of rotation on a resonant emission line such as
the \lya line?)

We can saythat the main effects of rotation on the \lya\ line morphology are:

@@

Addressing the second question we posed in the introduction (To what
extent is possible to constrain rotational kinematics from the \lya
emission line?)  we can say that as an application to observational data our results suggest that
rotation should also be considered as an explanation of the
non-vanishing \lya intensity at the line's center, which could change
the interpretation of recent observational results
\citep[e.g.][]{2017ApJ...844..171Y,2017A&A...608L...4R} that claim
instead that this flux constrains the escape fraction of \lya
radiation.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}\\
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.25\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity. } We show for each \tauh the dependency that
  the viewing angle $\theta$ has on the line's the
  valley intensity. $\vrot=100$\kms is fixed for all panels.
		\label{fig:valley_intensity}}
\end{figure*}

@@

\caption{\textbf{Comparison between simulations and observations.}  
The observational results correspond to the MUSE-Wide Survey
\citep{2017A&A...606A..12H}. The skewness and standard deviation from
the simulations summarize the results presented in Figures
\ref{fig:standard_deviation} and \ref{fig:skewness}.
  \label{fig:muse}}
\end{figure}

@@

The Monte Carlo code we use (CLARA) \citep{CLARA} follows the propagation of
individual photons through a neutral Hydrogen medium characterized by
its temperature, velocity field and global optical depth.
The code assumes an homogeneous density throughout the simulated
volume.
In the current implementation we neglect the influence of dust.
Our basic model is an spherical distribution of neutral hydrogen,
an approximation commonly used in the literature, as it explains a
wide variety of observational features
\citep{Ahn03,Verhamme06,Dijkstra06}.

@@

\begin{equation}
	v_{x}=\frac{x}{R}v_{\rm out}-\frac{y}{R}v_{\rm rot} ,
	\label{eq:vx}
\end{equation}

\begin{equation}
	v_{y}=\frac{y}{R}v_{\rm out}+\frac{x}{R}v_{\rm rot} ,
	\label{eq:vy}
\end{equation}

\begin{equation}
	v_{z}=\frac{z}{R}v_{\rm out},
	\label{eq:vz}
\end{equation}
%
where $x$, $y$ and $z$ are the cartesian position coordinates with the
origin at the sphere's center, $R$ is the radius of the sphere and the
direction of the angular velocity vector corresponds to the $\hat{k}$
unit vector.

@@

\begin{equation}
x' = x + \frac{\vec{v}_{\rm rot}\cdot\hat{k}}{v_{\rm th}}
\label{eq:shift_x}
\end{equation}
%
where $x'$ is the photon's new adimansional frequency, $x$ is the photon's
frequency after being procesed by the outflow, $v_{\rm rot}$ is the 
rotational velocity at the point of escape of the photon, $\hat{k}$ is
the photon's direction of propagation and $v_{\rm th}$ is the thermal
velocity of the sphere.

@@

In this section we discuss how the results we have presented can be
connected to the interpretation of observational data.

@@

To address the first question we posed in the introduction (\emph{ehat is then
the expected imprint of rotation on a resonant emission line such as
the \lya line?}) we can say that the main effects of rotation on the
\lya\ line morphology are:

@@

Addressing the second question we posed in the introduction (\emph{to what
extent is possible to constrain rotational kinematics from the \lya
emission line?})  we can say that as an application to observational data our results suggest that
rotation should also be considered as an explanation of the
non-vanishing \lya intensity at the line's center, which could change
the interpretation of recent observational results
\citep[e.g.][]{2017ApJ...844..171Y,2017A&A...608L...4R} that claim
instead that this flux constrains the escape fraction of \lya
radiation.
